---
title: "MACROCHARTS"
author: "Mateus Pereira and Ronaldo Torres"
date: ""
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
  header-includes:
  - \usepackage{float}
  - \usepackage{caption}
  - \usepackage{subfig}

bibliography: references.bib
---


<style>
body {
text-align: justify}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
\tableofcontents
\pagebreak
# MACROECONOMIA DE CURTO PRAZO

## Modelo IS-LM para economia fechada

$\qquad$ Nesta etapa, pasaremos a desenvolver "derivar" o modelo mais simples para a dinâmica IS-LM, que envolve uma economia fechada, para isso iniciaremos com a dedução do mercado de bens dessa economia. Na primeira etapa, será avaliado o gasto com investimento, que nesse modelo, é endógeno, pelo fato de ele estar condicionado a alterações na taxa de juros, em uma situação de de elevação da taxa de juros, menor será a taxa de investimento desejada ou planejada para está economia.

\begin{equation} 
I = \overline{I}- bi \hspace{1cm}  b>0 \label{fig:fig-sub}
\end{equation}


Em que na equação \ref{fig:fig-sub} se tem o gasto com investimento $I$ que é determinado pelo investimento autônomo $\overline{I}$, pela taxa de juros $i$ e pela sensibilidade do investimento em relação a taxa de juros $b$ ddd @dickey1979distribution



\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  \label{eq:binom}
\end{equation} 

You may refer to it using \ref{eq:binom}








# exemple, resolvi não apagar por ter informações relevantes:
Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))

# References
